### 2015-12-09 Projects/DelCo_2012/Report/DelCo_2012.tex
Update Delco 2012

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCoBurnBuildingDimensions}
	\caption{Delaware County, PA Burn Building Layout}
	\label{fig:Delaware_County,_PA_Burn_Building_Layout}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStoryDimensionsMetric}
	\caption{Floor Plan of the Test Structure.}
	\label{fig:Test_Structure_Floor_Plan}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.35\columnwidth]{../Figures/Pictures/Legend2}
	\caption{Instrumentation Legend.}
	\label{fig:Instrumentation_Legend}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/DelCoBurnBuildingInstrumentation}
	\caption{Instrumentation Schematic for the Gas Cooling Experiments.}
	\label{fig:Gas_Cooling_Instrumentation_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/DelCoSingleStoryInstrumentationDimensions}
	\caption{Instrumentation Schematic for the Fire Suppression Experiments.}
	\label{fig:Fire_Suppression_Instrumentation_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCoBurnBuildingFuelLoad}
	\caption{Burn Building Fuel Load.}
	\label{fig:Burn_Building_Fuel_Load}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/DelCoSingleStoryWoodFuelLoad}
	\caption{Wood Fuel Load Dimensions.}
	\label{fig:Wood_Fuel_Load_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/Furniture_Fuel_Load}
	\caption{Furniture Fuel Load Dimensions.}
	\label{fig:Furniture_Fuel_Load}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/DelCoSingleStoryFurnitureFuelLoad}
	\caption{Furniture Fuel Load Dimensions.}
	\label{fig:Furniture_Fuel_Load_Dimensions}
\end{figure}

>>>>

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Plain}
	\caption{Delaware County, PA Burn Building Layout}
	\label{fig:Delaware_County,_PA_Burn_Building_Layout}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Plain}
	\caption{Floor Plan of the Test Structure.}
	\label{fig:Test_Structure_Floor_Plan}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.35\columnwidth]{../Figures/Floor_Plans/PDFs/DelCo_2012_Instrumentation_Legend.pdf}
	\caption{Instrumentation Legend.}
	\label{fig:Instrumentation_Legend}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Instrumentation}
	\caption{Instrumentation Schematic for the Gas Cooling Experiments.}
	\label{fig:Gas_Cooling_Instrumentation_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Instrumentation}
	\caption{Instrumentation Schematic for the Fire Suppression Experiments.}
	\label{fig:Fire_Suppression_Instrumentation_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Pallets}
	\caption{Burn Building Fuel Load.}
	\label{fig:Burn_Building_Fuel_Load}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Pallets}
	\caption{Wood Fuel Load Dimensions.}
	\label{fig:Wood_Fuel_Load_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/Furniture_Fuel_Load}
	\caption{Furniture Fuel Load.}
	\label{fig:Furniture_Fuel_Load}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Furniture}
	\caption{Furniture Fuel Load Dimensions.}
	\label{fig:Furniture_Fuel_Load_Dimensions}
\end{figure}
